---
title: "getting-started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("imagefilterproject")
```

#install and load package magick
```
install.packages("magick")
library("magick")
```

#load package imagefilterproject

```
library(imagefilterproject)
```

#Load an image
```
my_image <- image_read("path_to_your_image.jpg")
```

#Convert image to raw RGB array (channels x width x height)
```
img_data <- image_data(my_image, channels = "rgb")
```

# THEN :
# If you are interested in a greyscale : 
```
convert_to_grey(c(255, 0, 0))
```

#Get dimensions
```
dims <- dim(img_data)
```

#Apply grayscale to each pixel`
```
for (x in 1:dims[2]) {
  for (y in 1:dims[3]) {
    rgb_pixel <- c(img_data[1, x, y], img_data[2, x, y], img_data[3, x, y])
    grey_pixel <- convert_to_grey(rgb_pixel)
    img_data[1, x, y] <- grey_pixel[1]
    img_data[2, x, y] <- grey_pixel[2]
    img_data[3, x, y] <- grey_pixel[3]
  }
}
```

#Reconstruct the image from modified pixel data
```
grey_image <- magick::image_read(img_data)
```

#Display the result
```
print(grey_image)
```

# If you are interested in a red filter : 
```
convert_to_red(c(255,0,0))
```
#Get dimensions`
```
dims <- dim(img_data)
```

#Apply red filter to each pixel
```
for (x in 1:dims[2]) {
  for (y in 1:dims[3]) {
    rgb_pixel <- c(img_data[1, x, y], img_data[2, x, y], img_data[3, x, y])
    red_pixel <- convert_to_red(rgb_pixel)
    img_data[1, x, y] <- red_pixel[1]  # Red
    img_data[2, x, y] <- red_pixel[2]  # Green = 0
    img_data[3, x, y] <- red_pixel[3]  # Blue = 0
  }
}
```
#Reconstruct the image from modified pixel data`
```
red_image <- magick::image_read(img_data)
```

#Display the red-filtered image
```
print(red_image)
```

# If you are interested in a green filter :
```
convert_to_green(c(255, 0, 0))
```

#Get dimensions
```
dims <- dim(img_data)`
```

#Apply green filter to each pixel
```
for (x in 1:dims[2]) {
  for (y in 1:dims[3]) {
    rgb_pixel <- c(img_data[1, x, y], img_data[2, x, y], img_data[3, x, y])
    green_pixel <- convert_to_green(rgb_pixel)
    img_data[1, x, y] <- green_pixel[1]  # Red = 0
    img_data[2, x, y] <- green_pixel[2]  # Green
    img_data[3, x, y] <- green_pixel[3]  # Blue = 0
  }
}
```

#Reconstruct the image from modified pixel data
```
green_image <- magick::image_read(img_data)
```

#Display the green-filtered image
```
print(green_image)
```

# If you are interested in a blue filter : 
```
convert_to_blue(c(255, 0, 0))
```

#Get dimensions
```
dims <- dim(img_data)  # 3 x width x height
```

#Apply blue filter to each pixel
```
for (x in 1:dims[2]) {
  for (y in 1:dims[3]) {
    rgb_pixel <- c(img_data[1, x, y], img_data[2, x, y], img_data[3, x, y])
    blue_pixel <- convert_to_blue(rgb_pixel)
    img_data[1, x, y] <- blue_pixel[1]  # Red = 0
    img_data[2, x, y] <- blue_pixel[2]  # Green = 0
    img_data[3, x, y] <- blue_pixel[3]  # Blue
  }
}
```

#Reconstruct the image from modified pixel data
```
blue_image <- magick::image_read(img_data)
```

#Display the blue-filtered image
```
print(blue_image)
```


